---
title: "Activity Monitoring - Project 1"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Read the files and load it into a table
activity <- read.csv("activity.csv")
```

## Histogram of the total number of steps taken each day

You can also embed plots, for example:

```{r hist, echo=FALSE}
steps_per_day <- aggregate(steps ~ date, activity, sum)
hist(steps_per_day$steps, col="yellow", xlab="Steps Taken", ylab ="Frequency", main="Histogram of Steps Taken")

```

## Mean and median number of steps taken each day

```{r mean_median, echo=FALSE}
mean_steps <- mean(steps_per_day$steps, na.rm = TRUE)
median_steps <- median(steps_per_day$steps, na.rm = TRUE)
mean_steps
median_steps
```


## Time series plot of the average number of steps taken

```{r interval steps, echo=FALSE}
library(ggplot2)
steps_per_interval <- aggregate(steps~interval+date, activity, mean)
g <- ggplot(steps_per_interval, aes(interval, steps))
g <- g+geom_line(color="blue") + ggtitle("Steps per interval")
print(g)
```

## The 5-minute interval that, on average, contains the maximum number of steps
```{r max steps, echo=FALSE}
max_steps_interval <- steps_per_interval[which.max(steps_per_interval$steps),1]
max_steps_interval
```


## Code to describe and show a strategy for imputing missing data

Number of missing value 
```{r missing value, echo=FALSE}
library(Hmisc)
missing_value<-length(which(is.na(activity$steps)))
missing_value
```
## Impute the missing value with mean 

```{r impute missing, echo=FALSE}
imputed_activity <- activity
imputed_activity$steps <- impute(imputed_activity$steps, fun=mean)
```

## Histogram of the total number of steps taken each day after missing values are imputed
```{r imputed hist, echo=FALSE}
steps_per_day_imputed <- aggregate(steps ~ date, imputed_activity, sum)
hist(steps_per_day_imputed$steps, col="blue", xlab="Steps Taken", ylab ="Frequency", main="Histogram of Steps Taken(Imputed)")
```



## Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r day hist, echo=FALSE}
weekdays <-c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
imputed_activity$dow <- weekdays.Date(as.Date(imputed_activity$date))
imputed_activity$weekday <-weekdays.Date(as.Date(imputed_activity$date)) %in% weekdays
# Subset data using weekday column value
imputed_activity_weekday <- subset(imputed_activity, imputed_activity$weekday==TRUE)
imputed_activity_weekend <- subset(imputed_activity, imputed_activity$weekday==FALSE)

#Plot weekday data
g <- ggplot(imputed_activity_weekday, aes(interval, steps))
g <- g+geom_line(color="red") + ggtitle("Steps per interval weekday")
print(g)

#Plot weekend data
g <- ggplot(imputed_activity_weekend, aes(interval, steps))
g <- g+geom_line(color="blue") + ggtitle("Steps per interval weekend")
print(g)
```


